Biden More Favorable Among Female, Black, Asian, Hispanic, Middle Eastern, and Non-gun Owning Voters in the 2020 US Presidential Election

### 2024-03-17 paper/paper.qmd
Fixed minor typos for final submission

Given that Biden and Trump are far apart on women’s issues, racial justice, and gun policy, we  chose `gender`, `race`, and `gunown` to be the predictor variables in our model. First, since we are interested in forecasting who a respondent is likely to vote for, we used “gender” instead of “gender_post” because it is representative of all adult Americans registered to vote rather than only adult Americans who voted. Second, we used “race” instead of variables by country or region to affirm that race is a social construct with no biological foundation. Third, we used “gunown” instead of variables about gun control because it captures broader opinions rather than specific policy proposals. After exploring the data in the previous section, we found differences in political preference based on these features and that it would be of interest to investigate further.

>>>>

Given that Biden and Trump are far apart on women’s issues, racial justice, and gun policy, we  chose `gender`, `race`, and `gunown` to be the predictor variables in our model. First, since we are interested in forecasting who a respondent is likely to vote for, we used `gender` instead of `gender_post` because it is representative of all adult Americans registered to vote rather than only adult Americans who voted. Second, we used `race` instead of variables by country or region to affirm that race is a social construct with no biological foundation. Third, we used `gunown` instead of variables about gun control because it captures broader opinions rather than specific policy proposals. After exploring the data in the previous section, we found differences in political preference based on these features and that it would be of interest to investigate further.
